---
title: "Memory Facial Threat"
author: "Graham Albert"
date: "June 9, 2019"
output:
  pdf_document: default
  html_document: default
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load glmm.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####T
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Rapid-Classification-Task-Data/master/Rating_MLM_Combine_20200901_Reduced.csv")
RCT<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(RCT)
```

####To determine variable names of the data set.
```{r}
names(RCT)[1]<-"ID"
names(RCT)

```

####Lets obtain some summary statistics.
```{r}
summary(RCT)
dim(RCT)
View(RCT)
```

####The dependent variable is categorical and dominance rating.
####We need to factor many of our varaibles.
```{r}
require(dplyr)
RCT = mutate(RCT,ID = as.factor(RCT$ID),Face_Shape = as.factor(RCT$Face_Shape), TrialNum= as.factor(RCT$TrialNum),Face_Set = as.factor(RCT$Face_Set), Morph_Type= as.factor(RCT$Morph_Type), Pic_Number  = as.factor(RCT$Pic_Number))
View(RCT)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(RCT$ID)
nlevels(RCT$Face_Shape)
nlevels(RCT$TrialNum)
nlevels(RCT$Face_Set)
nlevels(RCT$Morph_Type)
nlevels(RCT$Pic_Number)
```
####Now let's windsorize our continuous dependent variable RT.





####To recode recall and encoding so that the reference category changes.
```{R}
RCT$Face_Set = factor(RCT$Face_Set,
                             levels = c(1,2),
                             labels = c("London Face Set", "Nipissing University Face Set"))
table(RCT$Face_Set)
RCT$Morph_Type= factor(RCT$Morph_Type ,
                             levels = c(1,2),
                             labels = c("Feminized", "Masculinized"))
table(RCT$Morph_Type )

RCT$Face_Shape = factor(RCT$Face_Shape,
                             levels = c(1,2),
                             labels = c("Full Face", "Oval Face"))
table(RCT$Face_Shape)
```


###To obtain skew and kurtisosis statistics.
```{r}
require(psych)
describe(RCT$Dom)
```

####Lets proceed with a glmer in which ID is a random effect.
```{r}
options(scipen=9999)
require(lme4)
M1 = lmer(data=RCT,Dom~Morph_Type*Face_Shape*Face_Set+(1+Morph_Type|ID)+(1|TrialNum)+(1|Pic_Number))
summary(M1)
```
####To generate confidence interrval.
```{r}
confint(M1)
```


###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(M1)
```




####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(M1), resid(M1, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(M1)) 
qqline(resid(M1), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(M1)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(M1), c("M1"), LL = FALSE))
```



####To obtain the ICC for models 4.
```{r}
require(sjstats)
performance::icc(M1)
```

###To visual model.
```{r}
require(effects)
e <- allEffects(M1)
print(e)
plot(e)

```

# allEffects() returns a list, but for our model (where everything can interact with everything), there's only one element
```{r}
plot(e,multiline=TRUE,confint=TRUE,ci.style="bars"
     ,main="Effects of Face Morph on RT"
     ,xlab="Face Morph"
     ,ylab="Domininace Rating")
```
####Lets make a dataframe containing the data we need for the graph.
```{R}
e1 <- e[[1]]
e.df <- as.data.frame(e1)
```

####Lets use ggplot.
```{r}
require(ggplot2)
library(ggplot2)
library(extrafont)
library(magick)
loadfonts(device = "win")
#Save some time and store APA format-related code in an object so you can easily
#use it in multiple plots
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(size=12,family='serif'),
        legend.title=element_blank())
plt3 <- ggplot(e.df,aes(x=Morph_Type,y=fit,color=Face_Shape,shape=Face_Set,ymin=lower,ymax=upper)) + 
    geom_pointrange(position=position_dodge(width=.1)) + facet_wrap(~Face_Shape) +
    xlab("Face Morph") + ylab("Dominance Rating")+
    scale_colour_grey()+
    apatheme
plt3
ggsave(plt3, file = "Figure2.jpg", width =12, height = 7.5, dpi = 900)
```



###Lets see what happens when we plot the regression.
```{r}
plot(M1)
extractAIC(M1)
BIC(M1)
deviance(M1)
logLik(M1)
-2*logLik(M1)
```


####Let's use ggplot to create a regression plot for the data.
```{r}
require(sjPlot)
library(sjmisc)
plot_model(M1)
```

