---
title: "RCT Experiment"
author: "Graham Albert"
date: "October 30, 2018"
output: html_document
---

####To load required packarges
```{r}
require(curl) 
```
######loading data
```{r}
require(mice)
```
######missing data
```{r}
require(GPArotation)
```
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###modeling
```{r}
require(psych)##for EFA, and descriiptivves
require(BaylorEdPsych)####for missing value analysis
```


###To read in the data
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Rapid-Classification-Task-Data/master/RCT_MASTER_MERGED_LONG_20200918.csv")
RCT_ANOVAS_MASTER<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
View(RCT_ANOVAS_MASTER)
head(RCT_ANOVAS_MASTER)
names(RCT_ANOVAS_MASTER)
```

####To determine variable names of the data set.
```{r}
names(RCT_ANOVAS_MASTER)[1]<-"ID"
names(RCT_ANOVAS_MASTER)
View(RCT_ANOVAS_MASTER)
```





####To obtain the descriptive statistics includinag the skewness and kurtosis values of the variables.
```{r}
require(psych)
normalityassessment = describe(RCT_ANOVAS_MASTER_REDUCED[c(6,7)])
View(normalityassessment)
```




####To screening for missing values.
####To write a funtion to check for missng data.
```{r}
percentmiss=function(x){sum(is.na(x)/length(x))*100}
```


####To check for missing data by columns
```{r}
apply(RCT_ANOVAS_MASTER,2,percentmiss)
```

####To screen for multivariate outliers.
####To screen for multivariate outliers in the data set nomiss we will use mahalanobis distance statistic.
```{r}
mahal = mahalanobis(RCT_ANOVAS_MASTER[c(6,7)],
                    colMeans(RCT_ANOVAS_MASTER[c(6,7)], na.rm=TRUE),
                    cov(RCT_ANOVAS_MASTER[c(6,7)], use = "pairwise.complete.obs"))
cutoff = qchisq(1-0.001, ncol(RCT_ANOVAS_MASTER[c(6,7)])) #####generates cutoff score
ncol(RCT_ANOVAS_MASTER[c(6,7)]) #####determines df
table(mahal<cutoff)
```





###Multivariate assumption set up.
```{r}
set.seed(20)
random = rchisq(nrow(RCT_ANOVAS_MASTER_REDUCED[c(6,7)]),7)
fake = lm(random ~.,data=RCT_ANOVAS_MASTER_REDUCED[c(6,7)])###Predict random errors which are randomly distribued
standardized = rstudent(fake) ###Standarized residuals.
fitted = scale(fake$fitted.values) ###To scale the values
```
####To test for linearity.
```{r}
qqnorm(standardized)
abline(0,1)
```
####Based on  qq plot we have linearity.
####To test for normality.
```{r}
hist(standardized)
```
####Our variables are linear so we procede to test homogenity of vairance.
####Homogenity of Variance.
```{r}
plot(fitted, standardized)
abline(0,0)
abline(v=0)
```
####Get the names in the data set.
```{r}
names(RCT_ANOVAS_MASTER)
```

###To factor variables.
```{r}
RCT_ANOVAS_MASTER = mutate(RCT_ANOVAS_MASTER, ID=as.factor(ID), FACE_SET = as.factor(FACE_SET), MORPH_TYPE= as.factor(MORPH_TYPE),FACE_SHAPE = as.factor(FACE_SHAPE))
View(RCT_ANOVAS_MASTER)
```

```{r}
require(ez)
options(scipen=9999)
CON1_ANOVA = ezANOVA(data=RCT_ANOVAS_MASTER,
                dv =.(CON_2),
                wid =.(ID),
                within = .(MORPH_TYPE),
                between = .(FACE_SHAPE),
                observed = NULL,
                diff = NULL,
                reverse_diff = FALSE,
                type = 3,
                white.adjust = FALSE,
                detailed = FALSE,
                return_aov = FALSE)
CON1_ANOVA
```
